Method quality control

### 2018-01-31 analysis/analyses/4-method_characterisation/2_quality_control.Rmd
another fix for method characterisation

table %>% write_rds(figure_file("qc_checks.rds"))

table
```

@@

```{r, fig.width=10, fig.height=12}
aspect_position <- method_qc %>%
  filter(method_id == "SCORPIUS") %>%
  arrange(aspect_id) %>%
  group_by(aspect_id) %>%
  summarise(
    aspect_width = sum(score * weight),
    name = first(name)
  ) %>%
  mutate(
    aspect_end = cumsum(aspect_width),
    aspect_start = lag(aspect_end, 1, default=0),
    aspect_mid = aspect_start + (aspect_end - aspect_start)/2
  )

check_position <- method_qc %>%
  filter(method_id == "SCORPIUS") %>%
  arrange(aspect_id, check_id) %>%
  group_by(check_id) %>%
  summarise(
    check_width = score * weight,
    aspect_id = first(aspect_id)
  ) %>%
  left_join(aspect_position, by="aspect_id") %>%
  group_by(aspect_id) %>%
  mutate(
    check_start = aspect_start + lag(cumsum(check_width), default=0),
    check_end = aspect_start + cumsum(check_width)
  )

>>>>

table %>% write_rds(figure_file("qc_checks.rds"))
```

@@

```{r, fig.width=10, fig.height=12}
aspect_position <- method_qc %>%
  filter(method_id == "SCORPIUS") %>%
  arrange(aspect_id) %>%
  group_by(aspect_id) %>%
  summarise(
    aspect_width = sum(item_weight * weight),
    name = first(name)
  ) %>%
  mutate(
    aspect_end = cumsum(aspect_width),
    aspect_start = lag(aspect_end, 1, default=0),
    aspect_mid = aspect_start + (aspect_end - aspect_start)/2
  )

check_position <- method_qc %>%
  filter(method_id == "SCORPIUS") %>%
  arrange(aspect_id, check_id) %>%
  group_by(check_id) %>%
  summarise(
    check_width = item_weight * weight,
    aspect_id = first(aspect_id)
  ) %>%
  left_join(aspect_position, by="aspect_id") %>%
  group_by(aspect_id) %>%
  mutate(
    check_start = aspect_start + lag(cumsum(check_width), default=0),
    check_end = aspect_start + cumsum(check_width)
  )
